\begin{helper}
Fix a history cell \(C\), terminal set \(U\), recorded set \(R_h\), and a fixed
terminal scan order.  Assume the prefix-safety statement for the scan: when a
coordinate \(e\) is reached, staged-openness, touchedness, same-color
closedness, and recordedness of \(e\) are determined by the history and the
previously exposed terminal coordinates.  Let \(\omega\in C\) satisfy
\[
a\le |\noderef{TwoBiteStagedOpenPairs}(\omega,\varepsilon,I)|.
\]
Let \(R\) and \(B\) be the present red and blue staged-open supports, and
assume every present staged-open terminal coordinate lies in \(R\cup B\).
Then there is a finite set \(Z\subseteq U\), disjoint from \(R\cup B\), such
that every coordinate in \(Z\) is staged-open and absent in \(\omega\),
each member of \(Z\) is selected at a scan position where prefix-safety makes
the staged-open test measurable from the past, and
\[
\max(0,a-|R|-|B|)\le |Z|.
\]
\end{helper}
\begin{proof}
Let \(S=\noderef{TwoBiteStagedOpenPairs}(\omega,\varepsilon,I)\).  By the
terminal containment hypothesis, \(S\subseteq U\).  Split \(S\) into present
and absent coordinates.  The present coordinates are assumed to lie in
\(R\cup B\), so the absent staged-open coordinates contain
\[
S\setminus (R\cup B).
\]
The cardinality of this set is at least
\[
|S|-|R|-|B|.
\]
Since \(a\le |S|\), it is also at least \(a-|R|-|B|\) in the real-valued
sense.  If this number is nonpositive, take \(Z=\emptyset\).  Otherwise,
scan the fixed terminal order and choose the first
\(\lceil a-|R|-|B|\rceil\) coordinates belonging to
\(S\setminus(R\cup B)\).  This is possible by the preceding cardinality
bound.

The chosen set is contained in \(U\), is disjoint from \(R\cup B\), and every
chosen coordinate is staged-open and absent by construction.  Moreover, each
chosen coordinate is chosen at the moment it is encountered in the fixed
terminal order.  The prefix-safety hypothesis says that, at that moment, the
facts used to test staged-openness and exclusion from the recorded and
same-color-closed/touched predicates depend only on the history and earlier
terminal values.  Hence requiring the chosen coordinate to be absent still
charges a fresh terminal Bernoulli factor.  The number of chosen coordinates
is exactly the ceiling in the positive case and zero in the nonpositive case,
so in both cases
\[
\max(0,a-|R|-|B|)\le |Z|.
\]
\end{proof}
