\begin{helper}
Fix one blue support label \(B\) and one red label \(J\).  Let \(U\) be the
terminal coordinate set, let \(\mathcal P\) be the transcript family, and
for every realized branch/transcript pair \((\beta,\tau)\) write
\[
P_\tau,\qquad A_\tau,\qquad Z_\tau,\qquad F_{\beta,\tau}
\]
for the forced-present set, forced-absent set, selected-absence set, and
fixed present support \(B\cup R_{\beta,J}\).  Assume
\(F_{\beta,\tau}\subseteq P_\tau\).

Let \(\operatorname{scan}^{\mathrm{full}}\) be the deterministic ordered RISI
scan on complete terminal truth tables.  Let
\(\operatorname{scan}_{B,J}\) be one fixed residual-tree scan on residual
assignments \(A_{\rm res}\subseteq U\).  Assume the delete/reinsert
invariance of this residual-tree scan: on the residual cylinder attached to
a realized pair \((\beta,\tau)\),
\[
\operatorname{scan}_{B,J}(A_{\rm res})
 =
\operatorname{scan}^{\mathrm{full}}
  \bigl((A_{\rm res}\setminus Z_\tau)\cup F_{\beta,\tau}\bigr)
\]
whenever
\[
P_\tau\setminus F_{\beta,\tau}\subseteq A_{\rm res},\qquad
A_{\rm res}\cap(A_\tau\setminus Z_\tau)=\emptyset .
\]
This is one residual-tree rule after \(B,J\) are fixed: the candidate only
identifies which fixed support and selected set describe the cylinder being
checked.  The owner function itself is the single residual-tree scan applied
to the residual assignment, not a comparison between two candidate-dependent
compatibility relations.

Assume the reconstructed-scan stability furnished by the RISI reveal-order
calculation: whenever \(A_{\rm res}\subseteq U\),
\[
P_\tau\setminus F_{\beta,\tau}\subseteq A_{\rm res},\qquad
A_{\rm res}\cap(A_\tau\setminus Z_\tau)=\emptyset ,
\]
then
\[
\operatorname{scan}^{\mathrm{full}}
  \bigl((A_{\rm res}\setminus Z_\tau)\cup F_{\beta,\tau}\bigr)
  =(\beta,\tau).
\]
Then the single fixed-\((B,J)\) residual scan satisfies the exact stability
hypothesis needed by
\(\noderef{FixedSetHistoryCellFixedBJResidualOwnerConstruction}\):
\[
\operatorname{scan}_{B,J}(A_{\rm res})=(\beta,\tau)
\]
for every residual assignment in the displayed cylinder.
\end{helper}
\begin{proof}
The ordered scan used here is the blue-first/red-second reveal-order scan
from the paper.  The interface
\(\noderef{FixedSetHistoryCellRISIRevealOrderScanConstruction}\) records the
earlier-coordinate dependency sets for the scan and says that the scan output
is determined by the four tests read along the terminal order.  The
reconstructed-stability calculation
\(\noderef{FixedSetHistoryCellRISIResidualScanStability}\) applies this
interface to the complete terminal truth table
\[
(A_{\rm res}\setminus Z_\tau)\cup F_{\beta,\tau}.
\]
For coordinates in \(P_\tau\setminus F_{\beta,\tau}\), the residual cylinder
puts the coordinate in \(A_{\rm res}\), so the reconstruction is present
there.  For coordinates in \(F_{\beta,\tau}\), the reconstruction inserts
the fixed support.  For coordinates in \(A_\tau\setminus Z_\tau\), residual
avoidance keeps them out of \(A_{\rm res}\).  For coordinates in
\(Z_\tau\), the reconstruction deletes them before the full scan is run.
Thus the reconstructed truth table agrees with the realized witness on every
coordinate that the RISI dependency calculation permits the scan to read.

This is the point that was missing from the raw residual-scan formulation:
the selected coordinates are not left to influence the owner decision.  They
are charged outside the residual product tree as the selected
\((1-p)\)-factors, and the residual tree evaluates the ordered scan after
deleting \(Z_\tau\) and reinserting the fixed present support.  Hence a
selected coordinate may be red or blue; in either case it is removed once
from the residual assignment before the complete-truth-table scan is
evaluated.  The complete blue trace is still read first by the fixed
blue-first part of the reveal order, and the red support decoder for \(J\)
is then evaluated from that trace.

Now fix a realized pair \((\beta,\tau)\) and a residual assignment
\(A_{\rm res}\) satisfying
\[
P_\tau\setminus F_{\beta,\tau}\subseteq A_{\rm res},
\qquad
A_{\rm res}\cap(A_\tau\setminus Z_\tau)=\emptyset .
\]
By the delete/reinsert invariance of the fixed-\((B,J)\) residual tree scan,
\[
\operatorname{scan}_{B,J}(A_{\rm res})
 =
\operatorname{scan}^{\mathrm{full}}
  \bigl((A_{\rm res}\setminus Z_\tau)\cup F_{\beta,\tau}\bigr).
\]
The reconstructed-stability result just described gives that the right hand
side is \((\beta,\tau)\).  Therefore
\[
\operatorname{scan}_{B,J}(A_{\rm res})=(\beta,\tau).
\]
This conclusion is exactly the cylinder-stability input required by the
fixed residual-owner construction, and it is a statement about one
fixed-\((B,J)\) residual tree rather than about candidate-specific raw scans.
\end{proof}
