\begin{helper}
In a fixed history cell, assume each complete red terminal branch supplies a
blue exceptional set \(E_B(\beta)\) satisfying the closed-pair bound
\(|E_B(\beta)|\le 3\varepsilon_1 k^2\) and covering every blue present
staged-open coordinate of any regular independent completion of that branch.
Then there is one natural number \(N_B^{\mathrm{exc}}\), independent of the
branch, such that
\[
N_B^{\mathrm{exc}}\le 3\varepsilon_1 k^2,
\]
and every nonempty red branch admits a blue exceptional set of cardinality at
most \(N_B^{\mathrm{exc}}\) with the same blue coverage property.
\end{helper}
\begin{proof}
The argument is the color-swapped version of
\(\noderef{FixedSetHistoryCellGlobalRedExceptionalWitness}\).  The two-bite
sample space is finite, so the family of relevant complete red terminal
branches is finite.  For each such branch, choose the blue exceptional set
given by the branch hypothesis.

By \(\noderef{ClosedPairsBound}\), each chosen set has cardinality at most
\(3\varepsilon_1 k^2\), and the branch hypothesis gives its terminal
containment and blue-coverage property for all regular completions agreeing
with the branch on the embedding, recorded coordinates, and all red terminal
coordinates.  Let \(N_B^{\mathrm{exc}}\) be the maximum of these finitely many
cardinalities, or \(0\) if there are no relevant branches.  Since every
cardinality in the finite maximum is at most \(3\varepsilon_1 k^2\), the
maximum has the same bound.  Each branch keeps its chosen exceptional set,
now bounded by this global maximum, which proves the claim.
\end{proof}
