\begin{helper}
Fix a sample \(\omega\), a set \(I\), and a base vertex \(x\).  The closed
predicate has the following boundary properties.

First,
\[
v\in\noderef{TwoBiteX}(\omega,I,x)
\quad\Longleftrightarrow\quad
v\in I\ \hbox{and}\
v\in\noderef{TwoBiteLiftedNeighborhood}(\omega,x).
\]
Second, if \(x\) is staged-revealed and a same-color base coordinate \(c\) is
incident with \(x\), then
\(\noderef{TwoBiteProjectionPairTouched}(\omega,\varepsilon,I,c)\) holds.
Third, if a red tagged coordinate \(q\) lies in
\[
\noderef{TwoBiteBasePairs}
\bigl((\noderef{TwoBiteX}(\omega,I,x)).\pi_R^\omega\bigr),
\]
then \(\operatorname{red}(q)\) is
\(\noderef{TwoBiteProjectionPairClosed}(\omega,I,\operatorname{red}(q))\).
The analogous blue statement holds with \(\pi_B^\omega\).
\end{helper}
\begin{proof}
The first assertion is exactly the definition of
\(\noderef{TwoBiteX}\).  That definition filters \(I\) by membership in
\(\noderef{TwoBiteLiftedNeighborhood}(\omega,x)\), so an element survives the
filter if and only if it lies in \(I\) and in that lifted neighborhood.

For the second assertion, write the tagged coordinate \(c\) by cases.  If
\(x=\operatorname{red}(r)\) and \(c=\operatorname{red}(a,b)\), the incidence
hypothesis says \(a=r\) or \(b=r\).  Since \(x\) is staged-revealed, the
definition of \(\noderef{TwoBiteProjectionPairTouched}\) gives touchedness of
\(\operatorname{red}(a,b)\): in the first subcase the first endpoint is
revealed, and in the second subcase the second endpoint is revealed.  The
blue case is identical.  If \(x\) and \(c\) have different colors, the
incidence condition is false by definition, so there is no case to prove.

For the third assertion, suppose first that
\[
q\in
\noderef{TwoBiteBasePairs}
\bigl((\noderef{TwoBiteX}(\omega,I,x)).\pi_R^\omega\bigr).
\]
Unfolding \(\noderef{TwoBiteProjectionPairClosed}\) for the red tag, it is
enough to exhibit a base vertex whose red projection of \(X\) contains the
pair \(q\).  The vertex \(x\) itself is such a witness, by the displayed
membership.  Therefore
\(\operatorname{red}(q)\) is closed.  The blue assertion is word-for-word the
same, using the blue branch in
\(\noderef{TwoBiteProjectionPairClosed}\) and the blue projection of
\(\noderef{TwoBiteX}(\omega,I,x)\).
\end{proof}
