\begin{helper}
Let \(0<p<1\).  Let \(C\) be a history event in the two-bite sample space,
let \(\omega_0\in C\), let \(R\) be the recorded coordinate set, and let
\(U\) be a finite product coordinate set.  Assume that \(C\) is exactly the
cylinder consisting of samples with the same injection as \(\omega_0\) and
with the same \(\noderef{TwoBiteEdgeCoordinateValue}\)-truth values as
\(\omega_0\) on every coordinate in \(R\).  Assume every coordinate in \(R\)
and \(U\) is canonically oriented, and assume \(U\cap R=\emptyset\).  Then,
for every \(A\subseteq U\), the cylinder has nonzero
\(\noderef{TwoBiteEventProbability}\)-mass and
\[
\noderef{TwoBiteEventProbability}
\bigl(\{\omega:\omega\in C
\text{ and }
\noderef{TwoBiteEdgeCoordinateValue}(\omega,e)\Longleftrightarrow e\in A
\text{ for every }e\in U\}\bigr)
=
p^{|A|}(1-p)^{|U|-|A|}
\noderef{TwoBiteEventProbability}(C).
\]
\end{helper}
\begin{proof}
Unfold \(\noderef{TwoBiteEventProbability}\) and
\(\noderef{TwoBiteSampleWeight}\).  A sample consists of a red graph, a blue
graph, and an injection, and its weight is the product of the two
\(\noderef{GnpGraphWeight}\) factors and the
\(\noderef{UniformInjectionWeight}\) factor.  Each graph-weight factor is a
finite product over canonically oriented non-loop base-edge coordinates, with
factor \(p\) when the edge is present and factor \(1-p\) when it is absent.
The tagged red and blue coordinates are disjoint because they belong to
different graph factors.

The cylinder hypothesis says exactly that membership in \(C\) fixes the
injection to the injection of \(\omega_0\) and fixes precisely the recorded
coordinates in \(R\) to the truth table of \(\omega_0\).  It imposes no
condition on coordinates outside \(R\).  Since every coordinate in \(R\) and
\(U\) is canonically oriented, equality of the underlying graph coordinate
between an element of \(R\) and an element of \(U\) would force equality of the
tagged coordinates themselves.  This contradicts \(U\cap R=\emptyset\).  Thus
the product coordinates \(U\) are genuinely unconstrained by the cylinder.

Because \(\omega_0\in C\), the denominator cylinder is nonempty.  The
injection factor is positive for the fixed injection of \(\omega_0\).  Since
\(0<p<1\), each fixed recorded graph factor is either \(p\) or \(1-p\), hence
positive, and all unrestricted-coordinate sums are sums of nonnegative terms
with at least one positive term.  Therefore
\(\noderef{TwoBiteEventProbability}(C)\ne 0\).

Now fix \(A\subseteq U\).  In the numerator, the cylinder contributes exactly
the same fixed injection factor and the same fixed \(R\)-coordinate factor as
in the denominator.  The event on \(U\) contributes \(p\) for each coordinate
of \(A\) and \(1-p\) for each coordinate of \(U\setminus A\), so its total
factor is
\[
p^{|A|}(1-p)^{|U|-|A|}.
\]
All remaining coordinates are unrestricted both in the numerator and in the
denominator; summing over each such coordinate contributes \(p+(1-p)=1\).
Thus the numerator is exactly
\[
p^{|A|}(1-p)^{|U|-|A|}
\noderef{TwoBiteEventProbability}(C),
\]
as claimed.
\end{proof}
