\begin{helper}
Fix \(I\), a finite set \(R\) of terminal coordinates, and samples
\(\omega,\omega'\).  If \(R\) is exactly
\(\noderef{TwoBitePreTerminalRecordedPairs}(\omega,\varepsilon,I)\), if
\(\omega\) and \(\omega'\) have the same injection, and if they have the same
\(\noderef{TwoBiteEdgeCoordinateValue}\)-truth value on every coordinate of
\(R\), then
\(\noderef{TwoBiteStageRevealedVertex}(\omega,\varepsilon,I,x)\) holds if and
only if \(\noderef{TwoBiteStageRevealedVertex}(\omega',\varepsilon,I,x)\)
holds for every base vertex \(x\), and
\(\noderef{TwoBiteProjectionPairTouched}(\omega,\varepsilon,I,e)\) holds if
and only if
\(\noderef{TwoBiteProjectionPairTouched}(\omega',\varepsilon,I,e)\) holds for
every terminal coordinate \(e\).
\end{helper}
\begin{proof}
First apply \noderef{FixedSetPreTerminalReplayUniqueness} to the stated
hypotheses.  This confirms that the same set \(R\) is the pre-terminal
recorded set for \(\omega'\) as well as for \(\omega\).  The staged-revealed
conclusion, however, follows from the replay comparison before the terminal
recorded set is unfolded, so we spell out that comparison.

Projection containment agrees for \(\omega\) and \(\omega'\), because it is
computed only from the injection and the projected image of \(I\), and the
injections are equal.  The base fibers are also determined by the injection,
so \(F_1\) agrees for every base vertex.  To compare \(F_2\), fix vertices
\(x,y\).  If \(x\) and \(y\) have opposite colors, then
\(\noderef{TwoBiteBaseAdj}\) is false in both samples.  In the same-color
case, first separate the possibility that the two projected endpoints are
equal.  Then the red-red or blue-blue adjacency asked for by
\(\noderef{TwoBiteBaseAdj}\) is a loop adjacency in a simple graph, so it is
false in \(\omega\) and false in \(\omega'\).  Hence the adjacency predicates
agree in this endpoint-equal case, and there is no increasing terminal
coordinate to record.

Now assume the same-color projected endpoints are distinct.  Choose the
increasing ordered coordinate \(q\) between the two endpoints.  Whenever
\(y\) is in \(F_1\) and \(x\) is projection-contained,
\(\noderef{FixedSetPreTerminalF2QueriesRecorded}\) shows that the tagged
coordinate \(q\) lies in
\(\noderef{TwoBitePreTerminalRecordedPairs}(\omega,\varepsilon,I)\), hence in
\(R\).  The truth-table agreement on \(R\) gives the same graph-edge value in
\(\omega\) and \(\omega'\).  Therefore, for each fixed \(x\), the set of
\(y\)'s counted in \(\noderef{TwoBiteStageF2}\) is the same for the two
samples.  Thus \(\noderef{TwoBiteStageF2}\) agrees for every \(x\).

The definition of \(\noderef{TwoBiteStageRevealedVertex}\) is the disjunction
of three predicates: not projection-contained, \(F_1\), and \(F_2\).  All
three predicates have just been shown to agree between \(\omega\) and
\(\omega'\), so
\[
\noderef{TwoBiteStageRevealedVertex}(\omega,\varepsilon,I,x)
\Longleftrightarrow
\noderef{TwoBiteStageRevealedVertex}(\omega',\varepsilon,I,x)
\]
for every base vertex \(x\).

Finally unfold \(\noderef{TwoBiteProjectionPairTouched}\).  For a red tagged
coordinate \(q\), touched means that the red copy of \(q_1\) or the red copy
of \(q_2\) is staged-revealed.  For a blue tagged coordinate it is the
analogous statement with blue endpoints.  Since staged-revealed truth values
agree for every base vertex, each of these endpoint disjunctions agrees.
Therefore touched projection pairs agree for every terminal coordinate.
\end{proof}
