\begin{helper}
Fix finite branch labels \(\mathcal T\), transcript labels \(\mathcal P\),
a terminal coordinate set \(U\), a blue support \(B\), and red supports
\(R_\beta\).  For a transcript \(\tau\), write
\[
P_\tau,\qquad A_\tau,\qquad Z_\tau
\]
for its forced-present, forced-absent, and selected-absent coordinate sets.
Let \(\mathsf{Realized}(\beta,\tau)\) be the predicate that the
branch/transcript cell is actually realized.  Assume \(0\le p\le 1/2\),
\(|B|=u_B\), and \(B\subseteq U\).  For every realized
\((\beta,\tau)\), assume
\[
|R_\beta|=u_R,\qquad R_\beta\subseteq U,\qquad
B\cap R_\beta=\emptyset,\qquad
P_\tau,A_\tau\subseteq U,\qquad P_\tau\cap A_\tau=\emptyset,
\]
\[
B\cup R_\beta\subseteq P_\tau,\qquad Z_\tau\subseteq A_\tau,\qquad
L:=\max(0,a-u_R-u_B)\le |Z_\tau|.
\]

Assume the released residual cylinder mass
\(\rho_{\beta,\tau}\) is nonnegative on realized cells and is exactly the
product of the factors left after the mandatory present supports
\(B\cup R_\beta\) and the selected absences \(Z_\tau\) have been removed:
\[
\rho_{\beta,\tau}
=p^{|P_\tau|-u_R-u_B}(1-p)^{|A_\tau|-|Z_\tau|}.
\]
Assume also the fixed-support product-tree packing bound
\[
\sum_{\beta\in\mathcal T}
  \sum_{\tau\in\mathcal P:\mathsf{Realized}(\beta,\tau)}
    \rho_{\beta,\tau}\le 1.
\]
Then there is a finite residual leaf set \(\Lambda\), a leaf map
\(\iota(\beta,\tau)\in\Lambda\), and nonnegative leaf masses
\(\nu:\Lambda\to\mathbb R\) such that
\[
\sum_{\lambda\in\Lambda}\nu(\lambda)\le1,
\]
the leaf map is injective on realized branch/transcript pairs, and every
realized pair satisfies the termwise cylinder domination
\[
p^{|P_\tau|}(1-p)^{|A_\tau|}
\le
p^{u_R}p^{u_B}(1-p)^L\,\nu(\iota(\beta,\tau)).
\]
\end{helper}
\begin{proof}
Let the residual leaves be the realized pairs
\[
(\beta,\tau)\quad\hbox{with}\quad
\tau\in\mathcal P,\ \mathsf{Realized}(\beta,\tau),
\]
together with one dummy leaf.  Send a realized pair to its own leaf and send
all non-realized formal pairs to the dummy leaf.  Give the realized leaf
\((\beta,\tau)\) mass \(\rho_{\beta,\tau}\), and give the dummy leaf mass
\(0\).  This definition is single-valued because a realized leaf is indexed
by the pair itself.

The nonnegativity of \(\nu\) is the assumed nonnegativity of
\(\rho_{\beta,\tau}\), plus the dummy mass \(0\).  The total leaf mass is
exactly
\[
\sum_{\beta\in\mathcal T}
  \sum_{\tau\in\mathcal P:\mathsf{Realized}(\beta,\tau)}
    \rho_{\beta,\tau}
\]
plus the dummy contribution \(0\), so the fixed-support packing bound gives
\(\sum_\lambda\nu(\lambda)\le1\).  If two realized pairs have the same leaf,
then the leaf is the same indexed realized pair, hence both the branch label
and the transcript are equal.  This proves injectivity on realized cells.

It remains to verify the displayed domination.  Put \(q=1-p\).  From
\(0\le p\le1/2\), \(0\le q\le1\).  For a realized pair, the geometry gives
\[
B\cup R_\beta\subseteq P_\tau,\qquad |B|=u_B,\qquad |R_\beta|=u_R,
\]
and \(Z_\tau\subseteq A_\tau\).  Thus the full cylinder factor splits as
\[
p^{|P_\tau|}q^{|A_\tau|}
=
p^{u_R}p^{u_B}q^{|Z_\tau|}
  \bigl(p^{|P_\tau|-u_R-u_B}q^{|A_\tau|-|Z_\tau|}\bigr).
\]
The parenthesized factor is \(\rho_{\beta,\tau}\), which is the mass of the
realized residual leaf \(\iota(\beta,\tau)\).  Since
\(L\le |Z_\tau|\) and \(0\le q\le1\), we have \(q^{|Z_\tau|}\le q^L\).
Multiplying by the nonnegative fixed factors gives
\[
p^{|P_\tau|}q^{|A_\tau|}
\le
p^{u_R}p^{u_B}q^L\,\nu(\iota(\beta,\tau)).
\]
Substituting \(q=1-p\) proves the termwise cylinder domination.
\end{proof}
