\begin{helper}
Let \(n,m\) be natural numbers, let \(U_0,V_0,T\subseteq \operatorname{Fin} n\),
let \(\rho:\operatorname{Fin}n\to \operatorname{Fin}m\), and let
\(\eta:U_0\to \operatorname{Fin}m\).  Put
\[
S=\operatorname{im}(\eta),\qquad
R_i=\{v:\rho(v)=i\}.
\]
For each row \(i\), let \(d_i\) be the number of injective maps
\(f:R_i\to\operatorname{Fin}m\) satisfying \(f(u)=\eta(u)\) for every
\(u\in U_0\cap R_i\), and let \(g_i\) be the number of such maps which also
send every \(v\in T\cap R_i\) into \(S\).  Assume \(T\subseteq V_0\), assume
that every \(U_0\)-row is disjoint from every \(V_0\)-row, and assume every
\(d_i\) is nonzero.  Then every row quotient \(g_i/d_i\) is nonnegative and
\[
\frac{g_i}{d_i}\le
\left(\frac{|S|}{m}\right)^{|T\cap R_i|}
\]
for every row \(i\).
\end{helper}
\begin{proof}
Fix a row \(i\).  The numbers \(d_i\) and \(g_i\) are cardinalities of
finite sets, so they are nonnegative.  Since \(d_i\ne0\), in fact
\(d_i>0\) as a real number.  Therefore \(g_i/d_i\ge0\).

It remains to prove the upper bound.  First suppose that
\(T\cap R_i=\varnothing\).  Then the extra condition in the definition of
\(g_i\),
\[
\forall v\in R_i,\quad v\in T\Rightarrow f(v)\in S,
\]
is vacuous.  Hence the set counted by \(g_i\) is exactly the set counted by
\(d_i\), so \(g_i=d_i\).  Since \(d_i\ne0\),
\[
\frac{g_i}{d_i}=1.
\]
Also \(|T\cap R_i|=0\), so the right side of the desired inequality is
\((|S|/m)^0=1\).  The bound follows in this case.

Now suppose \(T\cap R_i\ne\varnothing\), and choose \(v_0\in T\cap R_i\).
Because \(T\subseteq V_0\), we have \(v_0\in V_0\).  We claim that
\(U_0\cap R_i=\varnothing\).  If \(u\in U_0\cap R_i\), then
\(\rho(u)=i=\rho(v_0)\), contradicting the row-disjointness hypothesis
applied to \(u\in U_0\) and \(v_0\in V_0\).  Thus no eta constraint is
present in row \(i\).  Consequently \(d_i\) is simply the number of
injective maps \(R_i\to\operatorname{Fin}m\), and \(g_i\) is the number of
such injective maps that send every element of \(T\cap R_i\) into \(S\).

To put this in the form of \(\noderef{OppositeProjectionRowInjectionCounting}\),
let \(q=|R_i|\) and choose a bijection
\(\alpha:\operatorname{Fin}q\to R_i\).  Let
\[
T'=\alpha^{-1}(T\cap R_i)\subseteq \operatorname{Fin}q,
\]
so \(|T'|=|T\cap R_i|\).  Apply
\(\noderef{OppositeProjectionRowInjectionCounting}\) with domain
\(\operatorname{Fin}q\), the constant red-coordinate map with value \(i\),
the same target set \(S\subseteq\operatorname{Fin}m\), and the subset
\(T'\).  Its denominator is nonzero because, under the bijection
\(\alpha\), its admissible injections are exactly injective maps
\(R_i\to\operatorname{Fin}m\), the set counted by \(d_i\), and \(d_i\ne0\).

Under the same reindexing, the child theorem's favorable numerator is
exactly the set counted by \(g_i\): the condition that every point of
\(T'\) lands in \(S\) translates through \(\alpha\) to the condition that
every point of \(T\cap R_i\) lands in \(S\), and there are no eta
constraints in this row.  Therefore
\(\noderef{OppositeProjectionRowInjectionCounting}\) gives
\[
\frac{g_i}{d_i}\le
\left(\frac{|S|}{m}\right)^{|T'|}
=\left(\frac{|S|}{m}\right)^{|T\cap R_i|}.
\]
This proves the desired upper bound for the nonempty case as well, and the
two cases cover every row.
\end{proof}
