\begin{helper}
Let \(n,m\) be natural numbers, let \(U_0,V_0,T\subseteq \operatorname{Fin} n\),
let \(\rho:\operatorname{Fin}n\to \operatorname{Fin}m\), and let
\(\eta:U_0\to \operatorname{Fin}m\).  Put
\[
S=\operatorname{im}(\eta),\qquad
R_i=\{v:\rho(v)=i\}.
\]
Let \(X_{\mathrm{all},\eta}\) be the set of injections
\(\phi:\operatorname{Fin}n\hookrightarrow \operatorname{Fin}m\times
\operatorname{Fin}m\) whose first coordinate is \(\rho\) and whose second
coordinate on \(U_0\) is \(\eta\).  Let \(X_{\mathrm{good},\eta}(T)\) be
the subset of \(X_{\mathrm{all},\eta}\) for which every \(v\in T\) has
second coordinate in \(S\).  For each row \(i\), let \(d_i\) be the number
of injective maps \(f:R_i\to\operatorname{Fin}m\) satisfying
\(f(u)=\eta(u)\) for every \(u\in U_0\cap R_i\), and let \(g_i\) be the
number of such row maps which also send every \(v\in T\cap R_i\) into
\(S\).  If \(|X_{\mathrm{all},\eta}|\ne0\), then
\[
|X_{\mathrm{all},\eta}|=\prod_i d_i,\qquad
|X_{\mathrm{good},\eta}(T)|=\prod_i g_i,
\]
every \(d_i\) is nonzero, and
\[
\frac{|X_{\mathrm{good},\eta}(T)|}{|X_{\mathrm{all},\eta}|}
=\prod_i\frac{g_i}{d_i}.
\]
\end{helper}
\begin{proof}
We first build the factorization for \(X_{\mathrm{all},\eta}\).  Given
\(\phi\in X_{\mathrm{all},\eta}\), define, for each row \(i\), a map
\[
f_i:R_i\to \operatorname{Fin}m,\qquad f_i(v)=(\phi(v))_2 .
\]
This map is injective on \(R_i\): if \(v,w\in R_i\) and
\(f_i(v)=f_i(w)\), then \((\phi(v))_1=\rho(v)=i=\rho(w)=(\phi(w))_1\)
and the second coordinates are equal, so \(\phi(v)=\phi(w)\); injectivity
of \(\phi\) gives \(v=w\).  If \(u\in U_0\cap R_i\), the defining eta
condition for \(X_{\mathrm{all},\eta}\) gives
\[
f_i(u)=(\phi(u))_2=\eta(u).
\]
Thus \(\phi\) determines a tuple \((f_i)_i\) counted by the factors \(d_i\).

Conversely, suppose that for every row \(i\) we are given a row map
\(f_i:R_i\to\operatorname{Fin}m\) counted by \(d_i\).  Define a global map
\[
\phi(v)=(\rho(v),f_{\rho(v)}(v)),
\]
where \(v\) is regarded as an element of the row \(R_{\rho(v)}\).  The first
coordinate of \(\phi(v)\) is \(\rho(v)\) by construction.  If
\(\phi(v)=\phi(w)\), then the first coordinates give \(\rho(v)=\rho(w)=i\);
viewing \(v\) and \(w\) in the common row \(R_i\), equality of the second
coordinates says \(f_i(v)=f_i(w)\), and rowwise injectivity gives
\(v=w\).  Hence \(\phi\) is injective.  If \(u\in U_0\), then \(u\in
R_{\rho(u)}\), and the eta condition on the row map \(f_{\rho(u)}\) gives
\((\phi(u))_2=\eta(u)\).  Therefore \(\phi\in X_{\mathrm{all},\eta}\).
The two constructions are inverse to one another, because both recover
exactly the same second coordinate in each row.  Hence
\[
|X_{\mathrm{all},\eta}|=\prod_i d_i .
\]

The same bijection restricts to the good sets.  Under the map
\(\phi\mapsto (f_i)_i\), the condition defining
\(X_{\mathrm{good},\eta}(T)\) is
\[
\forall v\in T,\quad (\phi(v))_2\in S.
\]
For \(v\in R_i\), the second coordinate \((\phi(v))_2\) is exactly
\(f_i(v)\).  Thus the displayed condition is equivalent, row by row, to
\[
\forall i,\ \forall v\in T\cap R_i,\quad f_i(v)\in S,
\]
which is precisely the extra condition counted by \(g_i\).  Therefore the
restricted bijection gives
\[
|X_{\mathrm{good},\eta}(T)|=\prod_i g_i .
\]

Now assume \(|X_{\mathrm{all},\eta}|\ne0\).  Since
\(|X_{\mathrm{all},\eta}|=\prod_i d_i\), the product of the real numbers
\(d_i\) is nonzero.  If some \(d_j\) were zero, then the whole product would
be zero, contradiction.  Thus every \(d_i\) is nonzero.  Using the two
product formulae and the fact that all denominator factors are nonzero, we
may divide factor by factor:
\[
\frac{|X_{\mathrm{good},\eta}(T)|}{|X_{\mathrm{all},\eta}|}
=\frac{\prod_i g_i}{\prod_i d_i}
=\prod_i\frac{g_i}{d_i}.
\]
This is the required quotient identity.
\end{proof}
